Hyperspectral tree defoliation modeling with a focus on feature-selection and model interpretation

### 2019-06-30 code/98-paper/journal/manuscript.tex
change acronyms to lower case

	% geringerer Zeilenabstand
	%\setlength{\itemsep}{-\parsep}
	\acro{AGB}{Above-Ground Biomass}
	\acro{ALS}{airborn laser scanning}
	\acro{ANN}{Artificial Neural Network}
	\acro{AUROC}{Area Under the Receiver Operating Characteristics Curve}
	\acro{BRT}{Boosted Regression Trees}
	\acro{CART}{Classification and Regression Trees}
	\acro{CNN}{convolutional neural networks}
	\acro{CV}{cross-validation}
	\acro{DAP}{digital aerial photogrammetry}
	\acro{ENM}{Environmental Niche Modeling}
	\acro{FPR}{False Positive Rate}
	\acro{FFS}{forward feature-selection}
	\acro{FS}{feature-selection}
	\acro{GAM}{Generalized Additive Model}
	\acro{GBM}{Gradient Boosting Machine}
	\acro{GLM}{Generalized Linear Model}
	\acro{ICGC}{Institut Cartografic i Geologic de Catalunya}
	\acro{IQR}{Interquartile Range}
	\acro{MARS}{Multivariate Adaptive Regression Splines}
	\acro{MEM}{Maximum Entropy Model}
	\acro{ML}{Machine-Learning}
	\acro{NDII}{Normalized Difference Infrared Index}
	\acro{NIR}{Near-Infrared}
	\acro{NRI}{Normalized Ratio Index}
	\acro{OLS}{ordinary least squares}
	\acro{LiDAR}{light detection and ranging}
	\acro{LOWESS}{Locally Weighted Scatter Plot Smoothing}
	\acro{PISR}{Potential Incoming Solar Radiation}
	\acro{PCA}{principal component analysis}
	\acro{PLS}{partial least-squares}
	\acro{RBF}{Radial Basis Function}
	\acro{RF}{Random Forest}
	\acro{RMSE}{Root Mean Square Error}
	\acro{RR}{Ridge Regression}
	\acro{RSS}{Residual Sum of Squares}
	\acro{SAR}{Synthetic Aperture Radar}
	\acro{SDM}{Species Distribution Modeling}
	\acro{SMBO}{Sequential-based Model Optimization}
	\acro{SVM}{Support Vector Machine}
	\acro{TPR}{True Positive Rate}
	\acro{VI}{vegetation index}
	\acro{XGBOOST}{extreme gradient boosting}
\end{acronym}

>>>>

	% geringerer Zeilenabstand
	%\setlength{\itemsep}{-\parsep}
	\acro{AGB}{above-ground biomass}
	\acro{ALS}{airborn laser scanning}
	\acro{ANN}{artificial neural network}
	\acro{AUROC}{area under the receiver operating characteristics curve}
	\acro{BRT}{boosted regression trees}
	\acro{CART}{classification and regression trees}
	\acro{CNN}{convolutional neural networks}
	\acro{CV}{cross-validation}
	\acro{DAP}{digital aerial photogrammetry}
	\acro{ENM}{environmental niche modeling}
	\acro{FPR}{false positive rate}
	\acro{FFS}{forward feature-selection}
	\acro{FS}{feature-selection}
	\acro{GAM}{generalized additive model}
	\acro{GBM}{gradient boosting machine}
	\acro{GLM}{generalized linear model}
	\acro{ICGC}{institut cartografic i geologic de catalunya}
	\acro{IQR}{interquartile range}
	\acro{MARS}{multivariate adaptive regression splines}
	\acro{MEM}{maximum entropy model}
	\acro{ML}{machine-learning}
	\acro{NDII}{normalized difference infrared index}
	\acro{NIR}{near-infrared}
	\acro{NRI}{normalized ratio index}
	\acro{OLS}{ordinary least squares}
	\acro{LiDAR}{light detection and ranging}
	\acro{LOWESS}{locally weighted scatter plot smoothing}
	\acro{PISR}{potential incoming solar radiation}
	\acro{PCA}{principal component analysis}
	\acro{PLS}{partial least-squares}
	\acro{RBF}{radial basis function}
	\acro{RF}{random forest}
	\acro{RMSE}{root mean square error}
	\acro{RR}{ridge regression}
	\acro{RSS}{residual sum of squares}
	\acro{SAR}{synthetic aperture radar}
	\acro{SDM}{species distribution modeling}
	\acro{SMBO}{sequential-based model optimization}
	\acro{SVM}{support vector machine}
	\acro{TPR}{true positive rate}
	\acro{VI}{vegetation index}
	\acro{XGBOOST}{extreme gradient boosting}
\end{acronym}
